Interval Probability for Fuzzy Quantum Theories

### 2016-06-15 prob.tex
prob.tex \begin{definition}[Ideal Measurement; Complement; Commutativity; Complete Set~\cite{Swart2013,peres1995quantum,Griffiths2003}]~ Updates...

\begin{definition}[Complement; Commutativity~\cite{peres1995quantum,Griffiths2003}]~

@@

@@

As mentioned above, each quantum event~$P$ will be associated with
an interval-valued probability~$\left[l,r\right]$. Notice that whenever
the magnetic field of the Stern-Gerlach is fixed, i.e., an complete
set of orthogonal projections are picked, measuring the spin is up
or down is exactly the same as tossing a coin. In another word, if
somebody claimed she is tossing a coin behind a veil, and only show
the resulting heads or tails, we cannot distinguish whether she has
really tossed a coin, or she has run an Stern-Gerlach experiment,
and show us the head, the tail, or the side of coin if the silver
atoms is spin up, spin down, or just hit the middle. Therefore, applying
interval

>>>>

\begin{definition}[Ideal Measurement; Complement; Commutativity;
Complete Set~\cite{Swart2013,peres1995quantum,Griffiths2003}]~ 

@@

\item A set of mutually orthogonal projections $P_{i}$ is called an ideal
measurement if it is a partition of the identity, i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$. 

@@

As mentioned above, each quantum event~$P$ will be associated with
an interval-valued probability~$\left[l,r\right]$. Notice that whenever
the magnetic field of the Stern-Gerlach is fixed, i.e., an ideal measurement
is picked, measuring the spin is up or down is exactly the same as
tossing a coin. In another word, if somebody claimed she is tossing
a coin behind a veil, and only show the resulting heads or tails,
we cannot distinguish whether she has really tossed a coin, or she
has run an Stern-Gerlach experiment, and show us the head, the tail,
or the side of coin if the silver atoms is spin up, spin down, or
just hit the middle. Therefore, applying interval-valued
